TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-07-04 paper/main.tex
MC.

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{TUDataset} for graph classification and regression. The collection consists of over 120 datasets of varying sizes from a wide range of applications. We provide Python-based data loaders, kernel, and graph neural network baseline implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{www.graphlearning.io}. The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
\end{abstract}

\section{Introduction}
Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics~\cite{Barabasi2004,Sto+2020} to image~\cite{Sim+2017} and social network analysis~\cite{Eas+2010}. To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges. In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Gil+2017}. However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results. 
Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.

\xhdr{Present work.} 
Here, we give an overview of \textsc{TUDataset}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{www.graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019}\footnote{\url{https://pytorch-geometric.readthedocs.io/en/latest/modules/datasets.html}} and \textsc{DGL}~\cite{Wan+2019}\footnote{\url{https://docs.dgl.ai/en/0.4.x/api/python/data.html}}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TUDataset}.

@@

\xhdr{Social networks.}
\citet{Yan+2015a} introduced several graph classification datasets derived from social networks. In the \textsc{Reddit} datasets, each graph represents a discussion thread, where nodes correspond to users, two of which are connected by an edge if one responded to a comment of the other. This graph model is used to derive several datasets, where the classification task is to distinguish either discussion-based and question/answer-based subreddits (\textsc{Reddit-Binary}) or predict the subreddit, where the thread was posted (\textsc{Reddit-Multi-5K} and \textsc{Reddit-Multi-12K}). \textsc{Collab} are datasets derived from scientific collaboration networks. Each graph is the ego-network of a researcher, and the task is to predict his research field, i.e., high energy, condensed matter, or astrophysics. Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations, and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
\citet{Rozemberczki2020} used similar approaches to obtain more massive social network datasets. \textsc{Reddit\_Threads} contains more than 200k graphs with the task to predict whether a thread is discussion-based. \textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services, and the task is to predict the gender and play behavior (single or multiple games) of the central user.
\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.

@@

\subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernels as well as GNN architectures. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TUDatasets}.  Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.

\subsection{Evaluation methods}\label{evalm} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNNs. First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps. We optimize GNNs end-to-end using \textsc{Adam}~\cite{Kin+2015}. To compute classification accuracies, we propose to use $10$-fold cross-validation, where we select $10\%$ of each training fold uniformly at random as validation set to optimize hyperparameters, e.g., the number of iterations, $C$ parameter, number of layers, feature dimension. We repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each). For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or the provided, fixed splits and report MAE (mean std. MAE, mean std. logMAE for multi-target regression, see \cite{Kli+2020}) over five runs.

@@

\begin{table*}[ht]\centering		
	\caption{Classification accuracies in percent and standard deviations on small-scale datasets.}
	\label{t2l}	
	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

@@

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			& \text{WL-OA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
			& \textsc{Gin-$\varepsilon$-JK} &  41.3 \scriptsize $\pm 1.8 \pm 6.7$       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
			\bottomrule
	\end{tabular}}
\end{table*}		
\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
	\label{t2ll}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\

@@

\xhdr{GNNs.} 
For comparison with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as neural baselines~\cite{Xu+2018}. For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK). We used mean pooling to pool the learned node embeddings to a graph embedding and used a $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP. We optimized the number of hidden units from $
\{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set. Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$. For both methods, we used the evaluation procedure described in~\cref{evalm} to optimize hyperparameters and compute accuracies. See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy},  \textsc{QM9}).

All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudatasets}.

\xhdr{Results and discussion.}
\cref{t2l,t2ll,neural_short_tt} summarize the results. On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines. However, it does not scale to large datasets, \cref{t2l}, as it relies on Gram matrix computation. Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baselines perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.}
Our results show that despite the extensive research on GNNs in recent years, classical graph kernels in combination with SVMs are still highly competitive in graph classification tasks.
\begin{table}[]\centering	
	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.05}
		\begin{tabular}{lccc}	\toprule
			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{3}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\		
			\bottomrule
	\end{tabular}}
\end{table}		
On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gine-$\varepsilon$} baseline.

@@

>>>>

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{TUDataset} for graph classification and regression. The collection consists of over 120 datasets of varying sizes from a wide range of applications. We provide Python-based data loaders, kernel, and graph neural network baseline implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{www.graphlearning.io}. The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudataset}.
\end{abstract}

\section{Introduction}
Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics~\cite{Barabasi2004,Sto+2020} to image~\cite{Sim+2017} and social network analysis~\cite{Eas+2010}. To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges. In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}. However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results. 
Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.

\xhdr{Present work.} 
Here, we give an overview of \textsc{TUDataset}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{www.graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019}\footnote{\url{https://pytorch-geometric.readthedocs.io/en/latest/modules/datasets.html}} and \textsc{DGL}~\cite{Wan+2019}\footnote{\url{https://docs.dgl.ai/en/0.4.x/api/python/data.html}}. To facilitate a standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TUDataset}.

@@

\xhdr{Social networks.}
\citet{Yan+2015a} introduced several graph classification datasets derived from social networks. In the \textsc{Reddit} datasets, each graph represents a discussion thread, where nodes correspond to users, two of which are connected by an edge if one responded to a comment of the other. This graph model is used to derive several datasets, where the classification task is to distinguish either discussion-based and question/answer-based subreddits (\textsc{Reddit-Binary}) or predict the subreddit, where the thread was posted (\textsc{Reddit-Multi-5K} and \textsc{Reddit-Multi-12K}). \textsc{Collab} are datasets derived from scientific collaboration networks. Each graph is the ego-network of a researcher, and the task is to predict their research field, i.e., high energy, condensed matter, or astrophysics. Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations, and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
\citet{Rozemberczki2020} used similar approaches to obtain more massive social network datasets. \textsc{Reddit\_Threads} contains more than 200k graphs with the task to predict whether a thread is discussion-based. \textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services, and the task is to predict the gender and play behavior (single or multiple games) of the central user.
\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.

@@

\subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernels as well as GNN architectures. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TUDataset}.  Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.

\subsection{Evaluation methods}\label{evalm} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNNs. First, for kernels, we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps. We optimize GNNs end-to-end using \textsc{Adam}~\cite{Kin+2015}. To compute classification accuracies, we propose to use $10$-fold cross-validation, where we select $10\%$ of each training fold uniformly at random as validation set to optimize hyperparameters, e.g., the number of iterations, $C$ parameter, number of layers, feature dimension. We repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each). For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or the provided, fixed splits and report MAE (mean std. MAE, mean std. logMAE for multi-target regression, see \cite{Kli+2020}) over five runs.

@@

\begin{table*}[ht]\centering		
	\caption{Classification accuracies in percent and standard deviations on small-scale datasets.}
	\label{t2l}	
	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{.95}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

@@

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			& \text{WL-OA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
			& \textsc{Gin-$\varepsilon$-JK} &  41.3 \scriptsize $\pm 1.8 \pm 6.7$       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
			\bottomrule
	\end{tabular}}
\end{table*}		
\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
	\label{t2ll}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.95}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star}}       & {\textsc{reddit\_threads}}      \\	\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\

@@

\xhdr{GNNs.} 
For comparison with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as neural baselines~\cite{Xu+2018}. For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK). We used mean pooling to pool the learned node embeddings to a graph embedding and used a $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP. For the smaller datasets of~\cref{t2l}, we optimized the number of hidden units from $
\{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set. For the mid-scale datasets, due to computation time constraints, we set the number of hidden units to $64$ and the number of layers to $3$. Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$, a maximum epoch number of $200$. For both methods, we used the evaluation procedure described in~\cref{evalm} to optimize hyperparameters and compute accuracies. See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy}, \textsc{QM9}). All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudatasets}.

\xhdr{Results and discussion.}
\cref{t2l,t2ll,neural_short_tt} summarize the results. On the small-scale datasets, see \cref{t2l}, the \textsc{WL-OA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines. However, it does not scale to large datasets, \cref{t2ll}, as it relies on Gram matrix computation. Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baselines perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.}
Our results show that despite the extensive research on GNNs in recent years, classical graph kernels in combination with SVMs are still highly competitive in graph classification tasks.
\begin{table}[]\centering	
	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.05}
		\begin{tabular}{lccc}	\toprule
			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{3}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\		
			\bottomrule
	\end{tabular}}
\end{table}		
On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gine-$\varepsilon$} baseline.

@@

\section{Dataset statistics}
